### 2024-04-24 paper/paper.qmd
update

In this paper, the dataset used for analysis was obtained from `measurementRectangles.json`. This dataset mirrors the measurements found in `measurements.csv`, including brand, style, gender specification (men or women), product name, brand size, waist size, fabric composition, price, and height and width measurements of jean pockets  (see @tbl-raw_data). Notably, the dataset contains a "pocketArea" column representing the area of the polygon generated from a pocket's measurements. However, it's important to note that the units of measurement for this area are not explicitly specified in the provided metadata. To determine the units, one must examine how the measurements were collected and processed. Since the measurements were processed using computer-generated calculations and intended for web display, it is possible that the pocket area is denoted in square centimeters (px²). However, without explicit confirmation from the data documentation or creators of the dataset, absolute certainty regarding the units of measurement remains elusive.

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-menwomen_table
#| layout-ncol: 2
#| tbl-cap: "Sample of Cleaned Men's and Women´s Data"

@@

head(women_jeans_data, 5) |>
  kable(
    format = "markdown",
    caption = "Women's Data",
    col.names = c("Price", "Pocket Area"),
    booktabs = TRUE
  )
```

To visually explore the relationship between pocket area and price for both men's (see @fig-price_per_pocket_men) and women's jeans (see @fig-price_per_pocket_women), scatter plots with regression lines were created.

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-price_per_pocket_men
#| fig-cap: "Jean Price vs Pocket Size (Men)"

# Create plot for men_jeans_data
men_jeans_plot <- ggplot(men_jeans_data, aes(x = pocket_area, y = price)) +
  geom_point(color = "blue") +
  geom_smooth(method = lm, se = FALSE) +
  labs(
    title = "Pocket Area and Price for Men's Jeans",
    x = "Pocket Area",
    y = "Price"
  ) +
  theme_classic()

@@

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-price_per_pocket_women
#| fig-cap: "Jean Price vs Pocket Size (Women)"

# Create plot for men_jeans_data
women_jeans_plot <- ggplot(women_jeans_data, aes(x = pocket_area, y = price)) +
  geom_point(color = "red") +
  geom_smooth(method = lm, se = FALSE) +
  labs(
    title = "Pocket Area and Price for Women's Jeans",
    x = "Pocket Area",
    y = "Price"
  ) +
  theme_classic()

# Standard deviation of price for women's jeans
women_price_sd <- sd(women_jeans_data$price)
```

@@

# Model
To gain further insights and make predictions about [], we will be implementing a linear regression model.

@@

Linear regression seeks to determine the optimal parameters $\beta_0$ and $\beta_1$ that minimize the discrepancies between predicted and observed prices across varying pocket areas in the dataset. Through this minimization process, the model constructs a line that most accurately represents the association between pocket area and price. Consequently, we can predict price values based on known pocket area measurements. This regression analysis sheds light on how pocket area influences the pricing of jeans for both men and women, offering valuable insights into the pricing dynamics within each gender category.

# Results

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-men_model_summary
#| tbl-cap: "Summary of Linear Regression Model for Men's Jeans"
# Fit a linear regression model for men's jeans
men_model <- lm(price ~ pocket_area, data = men_jeans_data)

# Print the summary table
kable(summary_table_men, caption = "Summary of Linear Regression Model for Men's Jeans", align = "c")

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-women_model_summary
#| tbl-cap: "Summary of Linear Regression Model for Women's Jeans"
# Fit a linear regression model for women's jeans
women_model <- lm(price ~ pocket_area, data = women_jeans_data)

# Print the summary table
kable(summary_table_women, caption = "Summary of Linear Regression Model for Women's Jeans", align = "c")
```

A scatterplot was generated to compare pocket area and price for both men's and women's jeans. Each gender category was represented by a distinct color in the plot. Additionally, linear regression lines were overlaid for each gender group to observe potential differences in the relationship between pocket area and price.

This visualization facilitated the comparison of how pocket area related to price for men's and women's jeans separately. By including separate regression lines for each gender, we could assess the direction and strength of the relationship between these variables within each group. The use of different colors for men and women aided in distinguishing between the two groups, enabling easy interpretation of the plot.
```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-price_per_pocket_gender
#| fig-cap: "Jean Price vs. Pocket Area Size per Gender"

@@

cleaned_area_data |>
  ggplot(aes(x = pocket_area, y = price, color = men_women)) + 
  geom_point() + 
  geom_smooth(method=lm, se=FALSE) + 
  labs(
    title = "Pocket Area and Price by Gender",
    x = "Pocket Area (square pixels)",
    y = "Price",
    color = "Gender"
  ) +
  scale_color_manual(values = c("blue", "red")) + theme_classic()
```

After visualizing the linear regression for both men's and women's jeans, I proceeded to analyze the results obtained from the regression models:

The linear regression models for both men's and women's jeans revealed interesting insights into the relationship between pocket area and price.

For men's jeans, the coefficient estimate for pocket area ($\beta_1$) is -0.002286, indicating a very small and statistically insignificant negative association between pocket area and price. This suggests that, on average, changes in pocket area do not have a significant impact on the price of men's jeans. The p-value associated with the pocket area coefficient is 0.6445, which is much greater than the typical significance level of 0.05. Additionally, the \( R^2 \) value, which measures the proportion of variance in the dependent variable explained by the independent variable, is very low at 0.005662. Overall, these results suggest that there is little evidence to suggest a meaningful relationship between pocket area and price for men's jeans.

In contrast, for women's jeans, the coefficient estimate for pocket area is -0.009345, also indicating a small negative association with price, although it is slightly larger in magnitude compared to men's jeans. However, like men's jeans, this coefficient is statistically insignificant with a p-value of 0.1804. The \( R^2 \) value for women's jeans is slightly higher at 0.04671, indicating that pocket area explains a slightly larger proportion of the variance in price compared to men's jeans. Despite this, the overall relationship between pocket area and price remains weak for women's jeans.

@@

@@

\appendix

# Appendix {-}

>>>>

In this paper, the dataset used for analysis was obtained from `measurementRectangles.json`. This dataset mirrors the measurements found in `measurements.csv`, including brand, style, gender specification (men or women), product name, brand size, waist size, fabric composition, price, and height and width measurements of jean pockets  (see @tbl-raw_data). Notably, the dataset contains a "pocketArea" column representing the area of the polygon generated from a pocket's measurements. However, it's important to note that the units of measurement for this area are not explicitly specified in the provided metadata. To determine the units, one must examine how the measurements were collected and processed. Since the measurements were processed using computer-generated calculations and intended for web display, it is possible that the pocket area is denoted in square centimeters (px²). However, without explicit confirmation from the data documentation or creators of the dataset, absolute certainty regarding the units of measurement remains elusive.
\newpage

@@

\newpage
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-menwomen_table
#| layout-ncol: 2
#| tbl-cap: "Sample of Cleaned Men's and Women´s Data"

@@

head(women_jeans_data, 5) |>
  kable(
    format = "markdown",
    caption = "Women's Data",
    col.names = c("Price", "Pocket Area"),
    booktabs = TRUE
  )
```
\newpage

To visually explore the relationship between pocket area and price for both men's and women's jeans scatter plots with regression lines were created (see Figure 1 and 2).

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-price_pocket
#| layout-ncol: 2
#| fig-cap: "Jean Price vs Pocket Size"

# Create plot for men_jeans_data
men_jeans_plot <- ggplot(men_jeans_data, aes(x = pocket_area, y = price)) +
  geom_point(color = "blue") +
  geom_smooth(method = lm, se = FALSE) +
  labs(
    title = "Pocket Size and Price for Men's Jeans",
    x = "Pocket Area",
    y = "Price"
  ) +
  theme_classic()

@@

# Create plot for men_jeans_data
women_jeans_plot <- ggplot(women_jeans_data, aes(x = pocket_area, y = price)) +
  geom_point(color = "red") +
  geom_smooth(method = lm, se = FALSE) +
  labs(
    title = "Pocket Size and Price for Women's Jeans",
    x = "Pocket Area",
    y = "Price"
  ) +
  theme_classic()

# Standard deviation of price for women's jeans
women_price_sd <- sd(women_jeans_data$price)

@@

@@

# Model
To gain further insights and make predictions about jeans pricing,  a linear regression model was implemented.

@@

The linear regression seeked to determine the optimal parameters $\beta_0$ and $\beta_1$ that minimize the discrepancies between predicted and observed prices across varying pocket areas in the dataset. Through this minimization process, the model constructs a line that most accurately represents the association between pocket area and price. Consequently, we can predict price values based on known pocket area measurements. This regression analysis sheds light on how pocket area influences the pricing of jeans for both men and women, offering valuable insights into the pricing dynamics within each gender category.

\newpage
# Results
A merged scatterplot was generated to compare pocket area and price for both men's and women's jeans. Each gender category was represented by a distinct color in the plot. Additionally, linear regression lines were overlaid for each gender group to observe potential differences in the relationship between pocket area and price (see @fig-price_per_pocket_gender).

This visualization facilitated the comparison of how pocket area related to price for men's and women's jeans separately. By including separate regression lines for each gender, we could assess the direction and strength of the relationship between these variables within each group. The use of different colors for men and women aided in distinguishing between the two groups, enabling easy interpretation of the plot.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-price_per_pocket_gender
#| fig-cap: "Jean Price vs. Pocket Size per Gender"

@@

cleaned_area_data |>
  ggplot(aes(x = pocket_area, y = price, color = men_women)) + 
  geom_point() + 
  geom_smooth(method=lm, se=FALSE) + 
  labs(
    title = "Pocket Size and Price by Gender",
    x = "Pocket Area",
    y = "Price",
    color = "Gender"
  ) +
  scale_color_manual(values = c("blue", "red")) + theme_classic()
```

After visualizing the linear regression for both men's and women's jeans, the results obtained from the regression models were analyzed.

For men's jeans, the coefficient estimate for pocket area ($\beta_1$) is -0.002286, indicating a very small and statistically insignificant negative association between pocket area and price. This suggests that, on average, changes in pocket area do not have a significant impact on the price of men's jeans. The p-value associated with the pocket area coefficient is 0.6445, which is much greater than the typical significance level of 0.05. Additionally, the \( R^2 \) value, which measures the proportion of variance in the dependent variable explained by the independent variable, is very low at 0.005662. Overall, these results suggest that there is little evidence to suggest a meaningful relationship between pocket area and price for men's jeans (see @tbl-men_lm).

In contrast, for women's jeans, the coefficient estimate for pocket area is -0.009345, also indicating a small negative association with price, although it is slightly larger in magnitude compared to men's jeans. However, like men's jeans, this coefficient is statistically insignificant with a p-value of 0.1804. The \( R^2 \) value for women's jeans is slightly higher at 0.04671, indicating that pocket area explains a slightly larger proportion of the variance in price compared to men's jeans. Despite this, the overall relationship between pocket area and price remains weak for women's jeans (see @tbl-women_lm).

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-men_lm
#| tbl-cap: "Summary of Linear Regression Model for Men's Jeans"

# Fit a linear regression model for men's jeans
men_model <- lm(price ~ pocket_area, data = men_jeans_data)

# Print the summary table
kable(summary_table_men, align = "c")

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-women_lm
#| tbl-cap: "Summary of Linear Regression Model for Women's Jeans"
# Fit a linear regression model for women's jeans
women_model <- lm(price ~ pocket_area, data = women_jeans_data)

# Print the summary table
kable(summary_table_women, align = "c")
```

@@

### 2024-04-24 scripts/02-data_cleaning.qmd
update

# Select the rows of interest
cleaned_area_data <-
  cleaned_area_data |>
  select(
    brand,
    men_women,
    price,
    pocket_area,
  )

cleaned_area_data

@@

```{r}
#### Save cleaned data ####
# save json cleaned data (pocket area measurements)

# Write the cleaned data frame to a CSV file
write_csv(cleaned_area_data, csv_file)
```

>>>>

# Filter the data to include only jeans for women and select columns
women_jeans_data <- cleaned_area_data |>
  filter(men_women == "women") |>
  select(
    price,
    pocket_area
  )

women_jeans_data

# Filter the data to include only jeans for men and select columns
men_jeans_data <- cleaned_area_data|>
  filter(men_women == "men") |>
  select(
    price,
    pocket_area
  )

men_jeans_data
```

```{r}
#### Save cleaned data ####
# Code referenced from: chat.openai.com

# Specify file paths
men_csv_file <- here::here("data/analysis_data/men_jeans_data.csv")
women_csv_file <- here::here("data/analysis_data/women_jeans_data.csv")

# Save men_jeans_data to a CSV file
write.csv(men_jeans_data, men_csv_file, row.names = FALSE)

# Save women_jeans_data to a CSV file
write.csv(women_jeans_data, women_csv_file, row.names = FALSE)

@@
